PDBF Testdokument

### 2015-03-31 test.tex
!
fixed bug with xref

\documentclass[10pt]{scrartcl}
\usepackage{PDBF}
\usepackage{wrapfig}
\usepackage[a4paper,vmargin={30mm,40mm},hmargin={28mm,28mm}]{geometry}

\title{PDBF Testdokument}
\author{
 Patrick Bender\\
  \texttt{s9pabend@stud.uni-saarland.de}
}
\date{\today{}, Saarbrücken}

@@

\DBSQLText{CREATE TABLE table1 (column1 INTEGER, column2 DATE, column3 FLOAT);}
\DBSQLFile{somedb.sql}
\DBSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtest, dim_time, dim_compiler, dim_dataset, dim_implementation, dim_layout, dim_query, dim_machine, fact_experiment}%

@@

    \begin{minipage}{\textwidth}
    \lineChart[width=1.0\textwidth, height=0.45\textwidth, xunit=Row Number, yunit={Runtime [in sec]}]{SELECT ROWNUM(), runtime FROM fact_experiment;}\\%
    \caption{Lot of points}
    \end{minipage}
\end{figure}

@@

\pivotTable[width=0.5\textwidth, height=0.8\textwidth, scale=0.5, rows={"Machine", "Table schema", "Query"}, aggregation=Minimum, aggregationattribute=Query time, aggregationBig=Minimum, aggregationattributeBig=Query time (in Sec)]
{SELECT
m.cpuarchitecture AS Machine,
IIF(d.tableschema = '(long a, long b)', 'long', IIF(d.tableschema = '(char a, char b)', 'char', IIF(d.tableschema = '(int a, int b)', 'int', 'n/a')))   AS [Table schema],
IIF(q.querytext = 'SELECT MIN(a+b) FROM t', 'Q1', 'Q2')     AS [Query],
c.compiler      AS Compiler,
c.optlevel      AS [Opt. level],
l.name          AS [Layout name],
CAST(COALESCE(IIF(i.templateparam, 'C', 'R'), 'n/a') AS VARCHAR) AS [Chunk size provi- ded at],
ROUND(v.runtime, 3) 		AS [Query time]
FROM fact_experiment AS v
    JOIN dim_machine m ON m.id = v.machineid
    JOIN dim_dataset d ON d.id = v.datasetid
    JOIN dim_compiler c ON c.id = v.compilerid
    JOIN dim_layout l ON l.id = v.layoutid
    JOIN dim_implementation i ON i.id = v.implementationid
    JOIN dim_query q ON q.id = v.queryid
ORDER BY m.id DESC, d.tableschema, q.querytext,
    c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize;}
{SELECT
m.cpu + ' (' +  m.cpuarchitecture + ')' AS Machine,
d.tableschema   AS [Table schema],
q.querytext     AS [Query],
c.compiler      AS Compiler,
c.optlevel      AS [Opt. level],
l.name          AS [Layout name],
CAST(COALESCE(l.chunksize, 'n/a') AS VARCHAR) AS [Chunk size (tuples)],
IIF(i.templateparam, 'Compile time', 'Runtime') AS [Chunk size provided at],
IIF(i.logscaleparam, 'Powers of 2', 'Multiples of 2') AS [Chunk sizes considered],
t.timestamp 	AS [Time of experiment],
ROUND(v.runtime, 3) 		AS [Query time (in Sec)]
FROM fact_experiment AS v
    JOIN dim_machine m ON m.id = v.machineid
    JOIN dim_dataset d ON d.id = v.datasetid
    JOIN dim_compiler c ON c.id = v.compilerid
    JOIN dim_layout l ON l.id = v.layoutid
    JOIN dim_implementation i ON i.id = v.implementationid
    JOIN dim_query q ON q.id = v.queryid
    JOIN dim_time t ON t.id = v.timeid
ORDER BY m.id DESC, d.tableschema, q.querytext,
    c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize;}

>>>>

\documentclass[10pt]{scrartcl}
\usepackage{PDBF}
\usepackage{wrapfig}
\usepackage{ngerman}
\usepackage[a4paper,vmargin={30mm,40mm},hmargin={28mm,28mm}]{geometry}

\title{PDBF Testdokument}
\author{
 Patrick Bender\\
  \texttt{s9pabend@stud.uni-saarland.de}
}
\date{\today{}, Saarbr"ucken}

@@

\DBSQLText{CREATE TABLE table1 (column1 INTEGER, column2 DATE, column3 FLOAT);}
\DBSQLFile{somedb.sql}
%\DBSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtest, dim_time, dim_compiler, dim_dataset, dim_implementation, dim_layout, dim_query, dim_machine, fact_experiment}%

@@

    \begin{minipage}{\textwidth}
    ~%\lineChart[width=1.0\textwidth, height=0.45\textwidth, xunit=Row Number, yunit={Runtime [in sec]}]{SELECT ROWNUM(), runtime FROM fact_experiment;}\\%
    \caption{Lot of points}
    \end{minipage}
\end{figure}

\clearpage

@@

~%\pivotTable[width=0.5\textwidth, height=0.8\textwidth, scale=0.5, rows={"Machine", "Table schema", "Query"}, aggregation=Minimum, aggregationattribute=Query time, aggregationBig=Minimum, aggregationattributeBig=Query time (in Sec)]
%{SELECT
%m.cpuarchitecture AS Machine,
%IIF(d.tableschema = '(long a, long b)', 'long', IIF(d.tableschema = '(char a, char b)', 'char', IIF(d.tableschema = '(int a, int b)', 'int', 'n/a')))   AS [Table schema],
%IIF(q.querytext = 'SELECT MIN(a+b) FROM t', 'Q1', 'Q2')     AS [Query],
%c.compiler      AS Compiler,
%c.optlevel      AS [Opt. level],
%l.name          AS [Layout name],
%CAST(COALESCE(IIF(i.templateparam, 'C', 'R'), 'n/a') AS VARCHAR) AS [Chunk size provi- ded at],
%ROUND(v.runtime, 3) 		AS [Query time]
%FROM fact_experiment AS v
%    JOIN dim_machine m ON m.id = v.machineid
%    JOIN dim_dataset d ON d.id = v.datasetid
%    JOIN dim_compiler c ON c.id = v.compilerid
%    JOIN dim_layout l ON l.id = v.layoutid
%    JOIN dim_implementation i ON i.id = v.implementationid
%    JOIN dim_query q ON q.id = v.queryid
%ORDER BY m.id DESC, d.tableschema, q.querytext,
%    c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize;}
%{SELECT
%m.cpu + ' (' +  m.cpuarchitecture + ')' AS Machine,
%d.tableschema   AS [Table schema],
%q.querytext     AS [Query],
%c.compiler      AS Compiler,
%c.optlevel      AS [Opt. level],
%l.name          AS [Layout name],
%CAST(COALESCE(l.chunksize, 'n/a') AS VARCHAR) AS [Chunk size (tuples)],
%IIF(i.templateparam, 'Compile time', 'Runtime') AS [Chunk size provided at],
%IIF(i.logscaleparam, 'Powers of 2', 'Multiples of 2') AS [Chunk sizes considered],
%t.timestamp 	AS [Time of experiment],
%ROUND(v.runtime, 3) 		AS [Query time (in Sec)]
%FROM fact_experiment AS v
%    JOIN dim_machine m ON m.id = v.machineid
%    JOIN dim_dataset d ON d.id = v.datasetid
%    JOIN dim_compiler c ON c.id = v.compilerid
%    JOIN dim_layout l ON l.id = v.layoutid
%    JOIN dim_implementation i ON i.id = v.implementationid
%    JOIN dim_query q ON q.id = v.queryid
%    JOIN dim_time t ON t.id = v.timeid
%ORDER BY m.id DESC, d.tableschema, q.querytext,
%    c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize;}
